% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[line,margin]{res} 

\usepackage{xparse}
\usepackage{hyperref}
\urlstyle{same}

\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.7in}

% sets default itemsep for itemize
\let\tempone\itemize
\let\temptwo\enditemize
\renewenvironment{itemize}{\tempone\itemsep -2pt}{\temptwo}

\begin{document} 

\NewDocumentCommand{\entry}{o o o}
  {
    \IfNoValueTF {#3}
      { {\noindent\bf #1}\dotfill\,#2\par }
      { {\noindent\bf #1,}\, #2\,\dotfill\,#3\par }
  }

\raggedright

  \begingroup
    \nointerlineskip
    \moveleft\hoffset\vbox{

      \large{\bf{Sasha Friedenberg}}\\
      \href{tel:6467081300}{+1-646-708-1300}\\
      \href{mailto:sashafriedenberg@gmail.com}{sashafriedenberg@gmail.com}
    }
  \endgroup

\begin{resume}
  \section{Related Experience}

    \entry
    [Platform Engineer]
    [The Infatuation / Zagat]
    [2019]

    \begin{itemize}

        \item Created roadmaps, prioritized work, and guided architecture for
          legacy editorial app, new user-generated content app, SMS-based
          restaurant recommendation concierge service, and editorialized
          restaurant finder app

        \item Increased deploy frequency from once a month to several times a
          day. Updated Kubernetes and Docker image to best practices (e.g.,
          reduced size of images from \textgreater500mb to \textless20mb).
          Integrated and optimized CI/CD pipeline on Google Cloud Build, and
          created local and staging dev environments.

        \item Optimized use of Google Maps API and reduced costs by
          \textdollar20/month. Integrated Firebase for user identity and sign-in.
          Integrated Stackdriver logging and metrics. Integrated Google
          CloudSQL.

    \end{itemize}

    \entry
    [Senior Software Engineer]
    [Etsy]
    [2016--2019]

    \begin{itemize}

        \item Improved speed of spell-corrected search results API from 700ms to
          300ms. Led A/B test using in-house experimentation platform to prove
          conversion win.

        \item Designed and built Ship, an internal tool that ingests GitHub data
          and automates app deployments across iTunes Connect, Google Play,
          email, and Slack. Maintains an audit trail, isolates credentials, and
          is SOX compliant.

        \item Developed holiday search and browse experience for native apps
          using in-house page layout engine allowing API-side control of native
          client experience.

        \item Led successful initiative to experiment with new improved
          machine-learning dataset for buyer app launch screen resulting in
          revenue increases.

        \item Coordinated across product and engineering to lead and implement
          user timezone settings to ensure push notifications are delivered at
          locale-appropriate times.

    \end{itemize}

  \section{Other\\ Experience}

    \entry
    [Workshop Instructor]
    [NYC Tech Talent Pipeline]
    [2020--present]

    \begin{itemize}

        \item Delivers data-structures and algorithms focused workshops to
          address skill and knowledge gaps amongst CUNY and NYC bootcamp
          students.

        \item Improves workshop curriculum and student selection to maximize
          tech industry jobs offered to underrepresented CUNY and bootcamp
          students.

    \end{itemize}

    \entry
    [Release Manager]
    [Etsy]
    [2014--2016]

    \begin{itemize}
        \item Transformed engineering culture by pioneering a two-week release
          schedule and a continuous-delivery model of app releases.

        \item Responsible for stable release of Etsy Android
          Buyer, Android Seller, iOS Buyer, and iOS Seller apps.

    \end{itemize}



  \section
  {Volunteering}

    \entry
    [Pursuit]
    [2019--present]

    \begin{itemize}

      \item Develops curriculum for and teaches workshops on using
        datastructures, problem solving, and big-O time \& space complexity to
        excel at traditional tech whiteboard interviews

      \item Mentored Pursuit fellow, providing guidance around job
        applications, whiteboard interviews, and resume preparation

    \end{itemize}

    \entry
    [CodeNation \& NYC Tech Talent Pipeline]
    [2018--present]

    \begin{itemize}

      \item Conducts mock behavioral and technical interviews for CS students
        and provides feedback and guidance to help prepare them future tech jobs

    \end{itemize}


  \section
  {Publications}

    \entry
    [How Etsy Ships Apps]
    [Etsy Engineering Blog, Code as Craft]
    [2017]

    \begin{itemize}

      \item
        \href
        {http://bit.ly/how-etsy-ships-apps}
        {http://bit.ly/how-etsy-ships-apps}

    \end{itemize}

  \section
  {Proficiencies}

    \begin{nohyphens}
    \begin{tabular}{l p{4in}}

      Languages &
      Bash,
      C,
      Go,
      Java,
      Objective-C,
      PHP,
      Python,
      Ruby,
      SQL
      \\

      Platforms &
      Android,
      Google Cloud Platform,
      Web Backend,
      iOS,
      \\

      Software & \raggedright
      Docker,
      Git,
      HTTP,
      Kubernetes,
      Linux,
      Protobufs,
      Unix
      \\

    \end{tabular}
    \end{nohyphens}

\end{resume}

\begin{center}
  \leftskip=-\sectionwidth \centerline{
    \tiny v\input{VERSION}
  }
\end{center}

\end{document} 



